Acceleration of plague outbreaks in the second pandemic

### 2020-08-29 supp.Rnw
in caption to Fig S8, mentioned tables where growth rate estimates are listed
tweaked caption to Table S5 and used correct colours for Sources in column 1

%
\begin{figure*}%[h!]
\begin{center}
  \includegraphics[width=\textwidth]{analysis/plots/probate_dates.pdf}
\end{center}
\caption[Wills written vs.\ probated]{Counts of wills written vs.\ wills probated during each of
  the four 14th century plague epidemics in London, based on wills
  probated in the Court of Husting \cite{Shar1889}. Smooth lines represent loess fits
with span=0.5 (shaded regions are 95\% confidence intervals).}
\label{F:willsVSprobates}
\end{figure*}
%

@@

%
\begin{figure*}%[h!]
\begin{center}
\scalebox{0.9}{
  \includegraphics{analysis/plots/seasonalgrowth.pdf}
}
\end{center}
\caption{Growth rate estimates for all the late epoch (1540--1680) London plague epidemics.  The growth rates shown for the major epidemics are the same as those in the right panel of \cref{F:combdata}. 
}
\label{F:seasonalgrowth}
\end{figure*}
%

@@

\begin{table*}
  \caption[Minor outbreak parameter estimates]{Parameter estimates for minor plague epidemics. Plague epidemics with $\hat r<1/\mathrm{yr}$ or $\hat r>100/\mathrm{yr}$, representing unreliable fits, are excluded; confidence limits that are $<0.1$ or $>200$ are replaced with {\tt NA}. See \Methodslink.}
  \footnotesize
  \rowcolors{2}{white}{verylightgray}
  \begin{center}
    \input{analysis/tables/minorparams.tex}
  \end{center}
  \label{tab:minorparams}
\end{table*}

>>>>

%
\begin{figure*}%[h!]
\begin{center}
  \includegraphics[width=\textwidth]{analysis/plots/probate_dates.pdf}
\end{center}
\caption[Wills written vs.\ probated]{Counts of wills written vs.\ wills probated during each of
  the four 14th century plague epidemics in London, based on wills
  probated in the Court of Husting \cite{Shar1889}. Smooth lines represent loess fits
with \texttt{span=0.5} (shaded regions are 95\% confidence intervals).}
\label{F:willsVSprobates}
\end{figure*}
%

@@

%
\begin{figure*}%[h!]
\begin{center}
\scalebox{0.9}{
  \includegraphics{analysis/plots/seasonalgrowth.pdf}
}
\end{center}
\caption{Growth rate estimates for all the late epoch (1540--1680)
  London plague epidemics.  The growth rates shown for the major
  epidemics are the same as those in the right panel of
  \cref{F:combdata}.  See \cref{tab:params,tab:minorparams}.}
\label{F:seasonalgrowth}
\end{figure*}
%

@@

\begin{table*}
  \caption[Minor outbreak parameter estimates]{Parameter estimates for
    minor plague epidemics (\emph{cf.}\/ \cref{F:seasonalgrowth}).
    Plague epidemics with $\hat r<1/\mathrm{yr}$ or
    $\hat r>100/\mathrm{yr}$, representing unreliable fits, are
    excluded; confidence limits that are $<0.1$ or $>200$ are replaced
    with {\tt NA}. See \Methodslink.}
  \footnotesize \rowcolors{2}{white}{verylightgray}
  \begin{center}
%% To get the colours used for each data type in plots:
%% source('plague_growth/analysis/plots/setcolours.R')
%% colvec1
%%    wills    parish      LBoM 
%%" #4D4D4D" "#1F78B4" "#E31A1C" 
%% t(col2rgb(colvec1))
%%        red green blue
%% wills   77    77   77
%% parish  31   120  180
%% LBoM   227    26   28
%% signif(t(col2rgb(colvec1))/255,3)
%%          red green  blue
%% wills  0.302 0.302 0.302
%% parish 0.122 0.471 0.706
%% LBoM   0.890 0.102 0.110
\definecolor{willsgrey}{rgb}{0.302,0.302,0.302}
\definecolor{parishblue}{rgb}{0.122,0.471,0.706}
\definecolor{LBoMred}{rgb}{0.890,0.102,0.110}
    \input{analysis/tables/minorparams.tex}
  \end{center}
  \label{tab:minorparams}
\end{table*}
